---
title: "SaraTyler_ggplot_walkthrough_20220401"
author: "Sara DeLaurentis"
date: "4/1/2022"
output: html_document
---

---
title: "ggplot_walkthrough_2022-04-01"
author: "Sara DeLaurentis"
date: "4/1/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## 
```{r }
library(tidyverse)
library(viridis)
library(hrbrthemes)
library(stringr)
#install.packages("viridis")
#install.packages("hrbrthemes")
#hrbrthemes::import_roboto_condensed()
#install.packages("wesanderson")
library(wesanderson)

#names(wes_palettes)
#getAnywhere(wes_palettes)


```

## 

mygraph = ggplot() +
  geom_line(data = set, aes(x = as.POSIXct(date.time, format = "%m/%d/%Y %H:%M"), y = value), size = 1.1) 


#10/31/2020 16:00

```{r }

#C:\Users\sbaue\coding\R_TEMPRY\Itasca_project_19-21\CLEAN_DATA_copy

m <- list.files("C:/Users/sbaue/coding/R_TEMPRY/Itasca_project_19-21/CLEAN_DATA_copy", pattern = "*.csv")
m

file_df <- data.frame(paths = m, name = str_replace(m, ".csv", ""), full_paths = list.files("C:/Users/sbaue/coding/R_TEMPRY/Itasca_project_19-21/CLEAN_DATA_copy", pattern = "*.csv", full.names = TRUE))

#selecting a subset of files
C2A <- file_df %>% filter(grepl("C2A",name))
view(C2A)
view(file_df)


data_list <- lapply(file_df$full_paths, read.csv)
str(data_list)
View(data_list)

sapply(n,FUN = ...,simplify = FALSE,USE.NAMES = TRUE)
?sapply

data_list <- lapply(seq_along(data_list), function(i){
  df <- data_list[[i]]
  sensor_name.df <- name %>% 
    str_split_fixed("_", n=5) %>% 
    as.data.frame()
  colnames(sensor_name.df) <- c("site", "rep", "position", "buttonID", "season")
  df$REP.name <- sensor_name.df$position
  df
})
view(df)

finalTable <- do.call(rbind, data_list)
finalTable$DataNumber <-as.factor(finalTable$DataNumber)
str(finalTable)
view(finalTable)
#write_csv(finalTable, "ULTRA_merge.csv") JUST TO SEE HOW BIG IT IS

ggplot(finalTable, aes(x=date.time, y = value, group = DataNumber, color = DataNumber)) +
  xlab("Group")+
  ylab("Data")

#for testing of one file in ggplot:
#data <- read.csv("C:/Users/sbaue/coding/R_TEMPRY/Itasca_project_19-21/CLEAN_DATA_copy/C2B_R3_lsurf_i110_2020.csv") 

view(data)

mygraph = ggplot() +
  geom_line(data = data, aes(x = as.POSIXct(date.time, format = "%m/%d/%Y %H:%M"), y = value), size = 1.1) 

#FOR POSSIBLE ADDITION OF SNOW/PRECIP:

#SNOW DATA
#NOAA <- read.csv("./NOAA_data_RAW.csv")
#NOAA$DATE <- as.Date(NOAA$DATE)
#UMN1 <- NOAA %>% 
#  filter(STATION == "USC00214106")

#mygraph = mygraph + geom_line(data = UMN1, aes(x = as.Date(DATE), y = SNWD), colour = "light blue", alpha = 0.5, lwd = (2.2))
print(mygraph)

#PLOT START AND STOP DATES
start <- as.POSIXct("2019-11-01") #set up start and end dates
end <- as.POSIXct("2020-08-01")

#PNG FILE DIMENSIONS
png(file = "testplot_0401.png", width = 2500, height = 1000, units = 'px')

mygraph = mygraph + ggtitle("C2B_test_plot") +
  ylab("Degrees C") +
  xlab("Date")


#axes adjustments and background adjustments

mygraph = mygraph + scale_x_datetime(date_breaks = "2 weeks", date_labels = "%m/%d/%y", limits = c(start,end)) + #set x-axis scale and label format
  scale_y_continuous(breaks = seq(-20,25,5), minor_breaks = NULL) #set the y scale
#seq arguments: seq(from (lowest value), to (highest value), interval)
args(scale_x_datetime)

mygraph = mygraph + 
  theme(axis.text.x = element_text(angle = 45, vjust = 0.9,
                                                     hjust = 0.9, size = rel(2))) +
  theme(axis.text.y = element_text(size = rel(2)))+
  coord_cartesian(xlim = c(start, end), ylim = c(-20, 35)) +
  theme(legend.position = c(0.9, 0.7)) 
  #theme(legend.justification = c("bottom", "right")) 


mygraph = mygraph + theme(plot.title = element_text(hjust = 0.5, size = rel(2.5), face = "bold")) +
  theme(axis.title = element_text(size = rel(2.75)))

mygraph = mygraph + 
  labs(subtitle = "INSERT SUBTITLE HERE", fill = "Sensor Position") +
  theme(plot.subtitle = element_text(size = rel(1.75), face = "italic", hjust = 0.5)) +
  theme(legend.text=element_text(size= rel(1.75)))+
  theme(legend.title=element_text(size = rel(1.9), face = "bold"))
#mygraph = mygraph + theme(plot.caption = element_text(size = rel(2))) + 
  theme(plot.margin = unit(c(20,45,5,20), "pt"))


?labs

print(mygraph)
dev.off()


```
##Create a dataframe to enable selection of .csv files.

```{r }
#create list of .csv files
m <- list.files("C:/Users/sbaue/coding/R_TEMPRY/Itasca_project_19-21/CLEAN_DATA_copy", pattern = "*.csv")
m

file_df <- data.frame(paths = m, name = str_replace(m, ".csv", ""), full_paths = list.files("C:/Users/sbaue/coding/R_TEMPRY/Itasca_project_19-21/CLEAN_DATA_copy", pattern = "*.csv", full.names = TRUE))

file_df

meta <- file_df$name %>%   #take the name column 
   str_split_fixed("_", n=5) %>% #split the strings, with _ as separator.
   as.data.frame() #COERCE
  colnames(meta) <- c("site", "rep", "position", "buttonID", "season") #
  meta$CLEAN = NULL 
  
  
data.list.df <- cbind(file_df, meta)
  #  temp_df <- temp_df[, c(6,1,2,3,4,5,7,8)] # column re-ordering if necessary
 
view(data.list.df)

```

#DATA SELECTION

```{r }

#select data:
C2A <- filter(data.list.df, site == "C2A")
#at some point I'm going to put the selection criteria as an input in a super-automated ggplot function.

view(C2A)
class(C2A)

```


### THIS IS THE CODE YOU'VE BEEN LOOKING FOR !!! ###
### VERY COOOlll lists ###

#What this does:

#1. Takes the dataframe we created from the names of the selected files, turns each ROW into ONE list element with "site", "rep", etc. as named elements contained inside.

#2. Uses lapply to read in the .csv files and attaches metadata.


```{r }
#Step 1: Turn each row of metadata into a list element with filenames, site, rep, etc. as named elements within.


files.meta.list <- list()                   # Create empty list


#Next, we can use a for-loop to store each row of our data frame as list element.

for(i in 1:nrow(C2A)) {   #for(each variable in the sequence "1 through the number of rows in C2A"):
                          
  file.meta.list[[i]] <- C2A[i , ]  #create an element in files.meta.list from each row found in C2A
}

#check it out: each element of the list (each [[x]]) contains the filenames and metadata, and they've maintained their column names as labels, so we can call out that named element when we want.
C2A
print(files.meta.list)


#Step 2: Use lapply to perform the following on each list element:
#Read .csv file given by the full_paths list element.
#Assign metadata columns based on the other named elements.
#Then, rbind all of those dataframes together for your finalTable

csv_LIST <- lapply(seq_along(files.meta.list), function(i){   #perform the given function along this list, each element in the list is the input.
  df <- read.csv(files.meta.list[[i]]$full_paths, header=TRUE, sep = ",") #create "df" by reading the .csv given by full_paths.
  df$site <- files.meta.list[[i]]$site    #next few rows are the addition of metadata columns based on the named element in the list. "Make a site column using the thing in the list at [[i]], that's labeled "site"
  df$rep <- files.meta.list[[i]]$rep
  df$position <- files.meta.list[[i]]$position
  df$buttonID <- files.meta.list[[i]]$buttonID
  df$season <- files.meta.list[[i]]$season
  df #VERY IMPORTANT. I don't know why, but without this call for the whole dataframe, you get left with just the last column you created.
  
  })

finalTable <- do.call(rbind, csv_LIST) ##JOIN TOGETHER
view(finalTable)

ggplot(finalTable, aes(x=as.POSIXct(date.time, format = "%m/%d/%Y %H:%M"), y=value, group = position, color = position)) + 
  geom_line() + 
  xlab("Date/Time") + 
  ylab("Temperature in C")


```
